Synthesising Complex Termination Arguments

### 2014-06-03 papers/termination/paper.tex
Added proofs.
Added Kalashnikov to the termination paper
+ introduction skeleton

\section{Introduction}
Church was BIG into program synthesis~\cite{church-synth}, so you know it's good stuff.

Something, something, Curry-Howard Isomorphism, something, something, programs-as-proofs.

@@

@@

>>>>

\section{Introduction}
{\bf First idea:}
Most reasearch on termination focuses on generating linear ranking functions for relations over mathematical integers/reals as opposed to 
bit-vectors (machine-level integers)/floating point. However, this may result in different behaviours than those observed in practice.

Illustration: two examples that terminate for mathematical integers/reals, but don't terminate for bit vectors/floats.
\begin{itemize}
\item[1.] q = q+y; y=y+1;
\item[2.] some floating point example
\end{itemize}

Hence, we work with bit vectors!

\noindent {\bf Second idea:}
Moreover, most works on termination assume restrictive transition relations and are concerned with linear ranking functions. However, the probability of a random program having a linear ranking function is very low ? (see Section ?).

We propose a general framework that does not assume the existence of linear ranking functions and can uniformly handle:
\begin{itemize}
\item lexicographic linear functions (no templates).
\item non-linear functions.
\item lexicographic non-linear functions.
\end{itemize}

Illustration: examples of programs that do not have linear ranking functions that we can handle.

\noindent {\bf Third idea:}
For this purpose, we rephrase the termination problem as a synthesis problem.
 As a direct consequence, the complexity of the method is dependent on the Kolmogorov complexity of the computed ranking function (+ it's not dependent on the size/number of variables of the analysed program). We empirically observe that most programs have ranking functions with low Kolmogorov complexity (see Section ?).

%Church was BIG into program synthesis~\cite{church-synth}, so you know it's good stuff.
%Something, something, Curry-Howard Isomorphism, something, something, programs-as-proofs.

@@

\begin{proof}
 Combinatorics.
\end{proof}

@@

\begin{proof}
 Trivial.
\end{proof}
